Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-01-03 lqg-strings.tex
Some more progress in the quantization
Started adding quantization into main file, made more progress on the sketch, and added Witten's book to .bib

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they're precisely the same as the ones of regular String Theory. What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
\begin{multline} \label{eqn:KG-Polyakov-solution-initial}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
\end{multline}
with $E_{p} = \sqrt{p^2 + \mu ^2}$. Reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation} \label{eqn:reality-consequence}
	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
\end{equation}

@@

>>>>

From our analysis of the inverse-area corrected Polyakov action, we got $D$ finite-space one-dimensional Klein-Gordon equations (\ref{eqn:X-Klein-Gordon-eqn}), with constraints given by eq\eqref{eqn:inverse-area-em-tensor}. The constraints are nothing new, they're precisely the same as the ones of regular String Theory. What's new in our analysis is the $\mu ^2$ term, which makes it so the solution is given by Fourier transform
\begin{multline} \label{eqn:KG-Polyakov-solution-initial}
	X^{\mu} (\tau , \sigma) = \frac{1}{2 \pi \alpha '} \sum _{p \in \mathbb{Z}} \frac{1}{2 E_{p}} \Big( \alpha ^{\mu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ \beta ^{\mu} _{p} \e ^{i (E_{p} \tau + p \sigma)} \Big) ,
\end{multline}
with $E_{p} = \sqrt{p^2 + \mu ^2}$. From here on, following an analogous procedure to the one found in \cite{Tong2009Lectures}, reality of $X^{\mu}$ implies $(X^{\mu})^{*} = X^{\mu}$, from which we get
\begin{equation} \label{eqn:reality-consequence}
	\beta ^{\mu} _{n} = (\alpha ^{\mu} _{- n})^{*} .
\end{equation}

@@

\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}

In this paper, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green_Schwarz_Witten_2012}
